# Create moving spectrogram
## Import audiofile
Here, we will use the `tico` file from `seewave`.

```{r}
library(seewave)
data(tico)
sound <- tico
```

## Create spectrogram

```{r spectro}
spectro(sound, palette= reverse.gray.colors.1)
```

## Export frames
We will calculate the number of frames needed for the movie, based on a given framerate (in fps).

```{r}
framerate <- 24
duration <- duration(sound)
nframes <- floor(duration * framerate)
```

For each frame, we will save a plot in a temporary folder with a vertical bar moving across the spectrum from frame to frame.

First, we will do a test with the bar.

```{r}
barpos <- 1 * framerate  # in frames
spectro(sound, palette= reverse.gray.colors.1)
abline(v = barpos / framerate)
```

Now we create a function to create all the frames.

```{r}
create.frames <- function(){
  for (i in 1:nframes){
    spectro(sound, palette= reverse.gray.colors.1)
    abline(v = i / framerate)
  }
}
```

## Compile movie
We will compile the movie using the `animation` package.

First, we need to export the sound file.

```{r}
if (!dir.exists("./cache")){
  dir.create("./cache")
}
sound_file <- file.path("./cache", "tico.wav")
savewav(wave = sound, filename = sound_file)
```


Now we compile the video.

```{r}
library(animation)

ani.options(interval= 1/framerate)
output <- "./cache/tico"
intermediate_output <- paste(output, "mp4", sep= ".")
saveVideo(expr = create.frames(), video.name = intermediate_output)
```

Finally, we add the audio.

```{r}
if (file.exists(final_output)){
  print("Output file already exists. Cannot overwrite it.")
}else{
  final_output <- paste(output, "avi", sep= ".")
  system2(command= "ffmpeg", args = paste(
    "-i", intermediate_output, "-i", sound_file, "-r", framerate, 
    "-codec copy -shortest", final_output
  ))
}
file.remove(intermediate_output)
```

